Volunteers in the Clouds: an Architecture for Low Cost and Potentially Massive Distributed Evolutionary Computation

### 2015-08-11 volunteer-clouds-ieee-ci-si.tex
Conclusion written
And closes #19

In this paper a client-server architecture for volunteer and distributed
evolutionary algorithms that uses the browser, termed {\sf NodIO} and
based on the {\sf NodEO} evolutionary algorithm library has been evaluated.

@@

Finally, the implementation needs some refinement in terms of
programming and also ease of use. Tools such as Yeoman might be used
to create a generator in which the user just has to create a fitness
function, with the rest of the framework wrapped around
automatically. All this, as the data used for this paper and the paper
itself, will be published with a free license in GitHub.

>>>>

In this paper two versions of a client-server architecture for volunteer and distributed
evolutionary algorithms that uses the browser, termed {\sf NodIO} and
based on the {\sf NodEO} evolutionary algorithm library has been evaluated.

@@

Finally, the implementation needs some refinement in terms of
programming and also ease of use. Tools such as Yeoman might be used
to create a generator in which the user just has to create a fitness
function, with the rest of the framework wrapped around
automatically. All this, as the data used for this paper and the paper
itself, has been published with a free license in GitHub at
\url{https://github.com/JJ/modeling-volunteer-computing}.
